Global case

### 2025-05-08 lipschitz 2025/Lipitschz.tex
update

	Recall the definition of Lipschitz continuity:
	under distance $d$, a function $f(x)$ is Lipschitz continuous with respect to constant $K$ if:
	\begin{align*}
		\forall \boldsymbol{x} \forall\boldsymbol{y} (|f(\boldsymbol{x}) -f(\boldsymbol{y}) |\leq K|\boldsymbol{x}-\boldsymbol{y}|)
	\end{align*} 
	In our practice of global robustness, we will consider the following weaker property with respect to a certain number $\varepsilon$:
	\begin{align*}
		\forall \boldsymbol{x} \forall\boldsymbol{y} &  (|\boldsymbol{x}-\boldsymbol{y}| \geq \varepsilon \implies|f(\boldsymbol{x}) -f(\boldsymbol{y}) |\leq K|\boldsymbol{x}-\boldsymbol{y}|\\
		&  |\boldsymbol{x}-\boldsymbol{y}| < \varepsilon \implies|f(\boldsymbol{x}) -f(\boldsymbol{y}) |\leq K\varepsilon)
	\end{align*} 
	In terms of the code, it is compute an optimization question respect to a certain number $\varepsilon$:	\begin{align}\label{global_robustness}
		\max_{|\boldsymbol{x}-\boldsymbol{y}| \leq \varepsilon} |f(\boldsymbol{x}) -f(\boldsymbol{y}) |
	\end{align} We can use this maximum value to estimate the Lipschitz constant.

@@

>>>>

	Recall the definition of Lipschitz continuity:
	under distance $d$, a function $f(x)$ is Lipschitz continuous with respect to constant $K$ if:
	\begin{align*}
		\forall \boldsymbol{x} \forall\boldsymbol{y} (|f(\boldsymbol{x}) -f(\boldsymbol{y}) |\leq K|\boldsymbol{x}-\boldsymbol{y}|)
	\end{align*} 
	In our practice of global robustness of computation, we will compute an optimization question respect to a certain number $\varepsilon$:	\begin{align}\label{global_robustness}
		\max_{|\boldsymbol{x}-\boldsymbol{y}| \leq \varepsilon} |f(\boldsymbol{x}) -f(\boldsymbol{y}) |
	\end{align} And this will lead to the following definition

@@

	From $\varepsilon$-diff bound, we cannot directly obtain a Lipschitz bound for the function, but we can get the following weaker bound:
